`flippant` --- An `R` package for the automated analysis of fluorescence--based

### 2017-01-02 inst/manuscript/manuscript.rmd
Minor yaml-header modification: keep processed md files for manual pandoc-processing outside of RStudio;

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon
  ^‡^ and Johannes Graumann ^†§\*^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  bookdown::pdf_document2:
    fig_caption: yes
    keep_tex: yes
    toc: no
  bookdown::word_document2:
    fig_caption: yes
    toc: no
csl: biomed-central.csl
bibliography: flippant.bib
---

>>>>

---
title: '`flippant` --- An `R` package for the automated analysis of fluorescence--based
  scramblase assays'
author: Richard J. Cotton ^†^, Birgit Ploier ^‡^, Michael A. Goren ^‡^, Anant K. Menon
  ^‡^ and Johannes Graumann ^†§\*^
date: '`r format(Sys.Date(), "%B %d,%Y")`'
output:
  bookdown::word_document2:
    fig_caption: yes
    toc: no
  bookdown::pdf_document2:
    fig_caption: yes
    toc: no
clean: no
csl: biomed-central.csl
bibliography: flippant.bib
---
